\name{}: Combining Bottom-up and top-down approaches through graph learning over interaction networks for drug-target-interaction prediction

### 2021-04-09 paper/main.tex
.

As DTI prediction is dependent on both drugs and proteins, there are
multiple ways of determining training, validation and testing sets of
pairs to evaluate each model. For cross-validation, we can perform the
split over DTI pairs, over drugs and over proteins, respectively,
where only in the latter two schemes unseen entities are guaranteed to
be shown to the model in the validation and testing
phase. Additionally, these schemes may have different expressiveness
and use different information in DTI prediction, as different
information is known in the training and testing phase.

>>>>

As DTI prediction is dependent on both drugs and proteins, there are
multiple ways of determining training, validation and testing sets of
pairs to evaluate each model. For cross-validation, we can perform the
split over DTI pairs, over drugs and over proteins, respectively; when
splitting over drugs or proteins, the entities (drugs or proteins) are
separated and all their associations included in the split.
Only when splitting by protein or drug are unseen entities guaranteed to
be shown to the model in the validation and testing
phase. The models resulting from the different splitting schemes may
have different expressiveness and exploit different information in DTI
prediction, as different information is known in the training and
testing phase.
